Convex Surrogates via Polyhedral Losses

### 2019-02-01 cvx-fin.tex
I don't even know what I did at this point

Recall that a \emph{halfspace-representation (H-rep)} of a closed polyhedral set $S$ in $d$ dimensions is a pair $(V,b)$ with $V \in \reals^{k \times d}$ and $b \in \reals^k$ such that $S = \{ w : Vw \leq b \}$.
We say an H-rep is \emph{tight} if for all $i=1,\dots,k$, there exists $w \in S$ such that $\langle V_i , w \rangle = b_i$.
\jessie{Imagine two planes in $\reals^3$ (constructing the H-rep) intersect on the line $\ell$ and a third plane only intersects the H-rep on $\ell$, but doesn't make the convex polytope any smaller.  Are we still ok with this being considered tight?  (I think I'm saying if each face is not full-dimensional?)}

>>>>

Recall that a \emph{halfspace-representation (H-rep)} of a closed polyhedral set $S$ in $d$ dimensions is a pair $(V,b)$ with $V \in \reals^{k \times d}$ and $b \in \reals^k$ such that $S = \{ w : Vw \leq b \}$.
We say an H-rep is \emph{tight} if for all $i=1,\dots,k$, there exists $w \in S$ such that $\langle V_i , w \rangle = b_i$.
